Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
minor change

---
title: "Pillar 1 - Sequential Pattern Mining"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
---

@@

```
We apply cspade followed by rule induction
```{r my_SR function}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_SR<- function(data){
 data %>%
  cspade(
    parameter = list(
      #include as many item sequences as possible
      support = 0,   # min support of a sequence
      maxsize = 1,   # max number of items of an element of a sequence
      maxlen  = 2,   # max number of element of a sequence
      mingap  = 1,   # min time difference between consecutive element of a sequence
      maxgap  = 1e4  # max time difference between consecutive element of a sequence
      #maxwin  = 1e4 # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      #include as many rules as possible
      confidence = 0,
      control    = list(verbose = FALSE)
      ) %>%
    clean_SR
}
```

@@

#Generating sequence rules:
SR_taken   <- my_SR(data = sequences$taken )
```

>>>>

---
title: "Pillar 1 - Sequential Pattern Mining"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

@@

}
```
We apply cspade followed by rule induction
```{r my_SR function}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_SR<- function(data){
 data %>%
  cspade(
    parameter = list(
      support = 0, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4 # max time difference between consecutive element of a sequence
      #maxwin  = 1e4  # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      confidence = 0, #we need to play with the parameters.
      control    = list(verbose = FALSE)
      ) %>%
    clean_SR
}
```

@@

#Generating sequence rules:
SR_taken   <- my_SR(data = sequences   )
```
